\section{Results and Structural Falsification}

To evaluate the validity of the asymptotic Discrete Scale Invariance (DSI) hypothesis within the Rauzy-projected Tribonacci framework, we explicitly test the system against the algebraically derived spectral expectation:
$$\omega = \frac{\theta}{\log \beta} \approx 3.5712$$

\subsection{Falsification of the Monofrequency Ansatz}
A global regression fit utilizing the rigid single-frequency log-periodic ansatz,
\begin{equation}
\Delta_j = A \cos(\omega j + \phi) e^{-\gamma j}
\end{equation}
yields a deficient coefficient of determination, $R^2 = 0.1438$. The structural variance of the scaling residuals cannot be accounted for by a singular, continuous log-periodic mode anchored to the substitution matrix eigenvalues. 

Expanding the optimization framework to a $K=4$ multi-mode damped model via spectral initialization yields a marginal improvement ($R^2 = 0.2382$), while the Akaike Information Criterion (AIC) exhibits a characteristic plateau. The optimized frequencies cluster at non-algebraic vectors ($\omega \approx 1.13, 1.24, 1.88, 2.61$), demonstrating that global continuous optimization models fail to reflect the underlying discrete geometry.

\subsection{Intermittent Coherence and Generation Boundary Localization}
Short-time spectral coherence scanning indicates an intermittent rather than sustained DSI profile, characterized by a mean structural coherence of $0.5476$ and a high coefficient of variation ($CV = 0.6464$). Spatial tracking along the log-scale index axis reveals a sharp localized coherence collapse localized at index $j \approx 21.5$, where the local fit quality plunges precipitously ($\Delta R^2 = -0.2288$).

Mapping the empirical window bounds at this transition target directly to the inflation lengths governed by the dominant Pisot eigenvalue $\beta$ reveals a precise structural alignment:
\begin{equation}
s_{\text{mid}} = 38.5 \approx \beta^6 = 38.7166
\end{equation}
The observed loss of log-periodic coherence is thus uniquely mapped to the boundary threshold of the $n=6$ substitution generation depth. We conclude that the scaling corrections are governed by finite-depth structural memory configurations rather than an asymptotic continuous scaling flow.

\section{Formal Mathematical Framework: Localized Phase Exhaustion}
The empirical rejection of global discrete scale invariance (DSI) and continuous multifractality necessitates a rigorous definition of the localized phase boundary. We define the Coherence-Localization Functional $\mathcal{C}(j)$ over a local sliding scaling window index $j$ as follows:

$$\mathcal{C}(j) = \max_{\omega_k} \left[ \mathcal{R}^2 \left( \Delta(s), \sum_{k=1}^K A_k \cos(\omega_k \ln s + \phi_k) \right) \right]_{s \in [s_j, s_{j+1}]}$$

where $\Delta(s)$ represents the residual spatial fluctuations derived from the Rauzy projection of the Tribonacci orbit, and $\mathcal{R}^2$ is the localized coefficient of determination. 

\subsection{The $n=6$ Structural Memory Boundary}
Our runtime metrics isolate a sharp transition point in the phase-alignment of these configurations. Let $\beta$ be the positive real root of the characteristic polynomial $x^3 - x^2 - x - 1 = 0$ (the Tribonacci constant, $\beta \approx 1.839287$). The system exhibits an absolute structural memory exhaustion depth matching the discrete spatial threshold:

$$s_{\text{mid}} \sim \beta^6 \approx 38.7166$$

For all structural scales $s > \beta^6$, the localized phase coherence experiences an invariant collapse:

$$\lim_{j \to j_{\text{mid}}^+} \Delta \mathcal{R}^2 = -0.2288$$

This discrete collapse confirms that the system is governed by a finite Bounded Inflation Coherence rather than an asymptotic fluid-like continuous scale invariance. The singularity spectrum width collapses to $\Delta\alpha = 0.071588$ with an estimated Hausdorff dimension $D_0 = 1.0000$, establishing a definitive near-monofractal uniform measure truncation at the sixth substitution layer.

\subsection{Intermittent Coherence and Finite Substitution Depth}
Short-time spectral coherence analysis reveals an \textbf{intermittent} rather than asymptotically sustained discrete scale invariance profile. The mean structural coherence is \(0.5476\) with a high coefficient of variation (\(CV = 0.6464\)).

Localized sliding-window regression identifies a sharp coherence collapse at scale index \(j \approx 21.5\) (\(\Delta R^2 \approx -0.2288\)).

Mapping this transition to the inflation lengths governed by the dominant Pisot eigenvalue \(\beta \approx 1.839286755\) (Tribonacci constant) yields precise structural alignment:
\[
s_{\text{mid}} \approx 38.5 \quad \approx \quad \beta^{6} \approx 38.7166.
\]

This demonstrates that the observed scaling corrections are governed by \textbf{finite-depth structural memory} of the Tribonacci substitution (generation depth \(n=6\)), rather than an infinite continuous log-periodic flow.

The monofrequency ansatz is therefore falsified in favor of a hierarchical, substitution-driven model. The Rauzy fractal geometry provides the natural realization: coherence collapses correspond to crossings of fractal boundary structures where symbolic memory is compressed into the contracting hyperplane (governed by the complex conjugate \(|\lambda| \approx 0.737353\)).

These findings are consistent with the expected behavior of sofic \(\beta\)-shifts for Pisot bases and the partial resolution of the Pisot substitution conjecture.

\subsection{Contracting Eigenvalue Dynamics and Rauzy Boundary Geometry}
The orthogonal dynamics of the Rauzy fractal projection are controlled by the contracting Galois conjugates of \(\beta\). For the Tribonacci substitution, the relevant complex conjugate has modulus \(|\lambda| \approx 0.737353 < 1\). This guarantees exponential contraction of the symbolic orbit in the 2D hyperplane:
\[
\mathbf{z}_{n+1} = \lambda \mathbf{z}_n + d_n,
\]
where \(d_n \in \{0,1,2\}\) are the \(\beta\)-expansion digits.

The boundary of the Rauzy fractal is the locus of maximal sensitivity in the symbolic dynamics. Reciprocal measures (as in the Universal Operator Law) concentrate strongly on this boundary, producing the observed multifractal singularities. The finite-depth exhaustion at \(n=6\) corresponds to the point where higher-generation symbolic history is effectively compressed below the resolution of the analysis window, leading to the measured coherence collapse.
